Homicide Increases in the COVID-19 Era

### 2025-02-28 Draft2.qmd
Added Marco's charts to the second draft

## geom_jitter

## Plot 5

>>>>

## geom_jitter
## geom_jitter

```{r, echo=FALSE}
ggplot(crime_la, aes(x = DateParsed, y = Vict.Sex, color = Vict.Sex)) +
  geom_jitter(alpha = 0.4, width = 0.2) +
  labs(title = "Crime Over Time by Gender",
       x = "Date",
       y = "Gender") +
  theme_minimal()

## Density Plot

crime_la$Hour <- as.numeric(format(crime_la$DateParsed, "%H"))

ggplot(crime_la, aes(x = Hour, fill = ..density..)) +
  geom_density(alpha = 0.5, color = "black") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(title = "Crime Density Per Hour",
       x = "Hour",
       y = "Density") +
  theme_minimal()
